The Mass Distribution of Stellar-Mass Black Holes

### 2010-06-29 paper.tex
Acknowledgements stub, and updated author list.

\author{Andrew Cantrell \and Laura Kreidberg \and Rachel Macdonald
  \and Charles Bailyn}
\affil{Yale University Department of Astrophysics\\P.O. Box
  208101, New Haven, CT 06520}
\email{andrew.cantrell@yale.edu, laura.kreidberg@yale.edu,
  rachel.macdonald@yale.edu, charles.bailyn@yale.edu}

@@

>>>>

\author{Andrew Cantrell \and Laura Kreidberg \and Charles Bailyn}

\affil{Yale University Department of Astrophysics\\
  P.O. Box 208101, New Haven, CT 06520}

\email{andrew.cantrell@yale.edu, laura.kreidberg@yale.edu,
  charles.bailyn@yale.edu}

@@

\acknowledgements

This work was supported by grant XXX.  WMF would like to thank Ilya
Mandel for illuminating discussions and encouragement.
